Reproduction frequency and offspring survival decline in elephant seals past prime age

### 2024-07-09 paper/paperv3.qmd
updating the biological age figure

ggplot(bioage_pred_pop, aes(bioage, predicted)) +
  geom_ribbon(aes(fill = bioage_cat, ymin = conf.low, ymax = conf.high), 
              alpha = 0.2) +
  geom_line(aes(color = bioage_cat), linewidth = 1.2) +
  geom_line(aes(color = bioage_cat),
            bioage_pred_wgt, 
            linewidth = 1.2,
            linetype = "dotted") +
  geom_pointrange(aes(y = perc_breed, 
                      ymin = perc_breed - se, 
                      ymax = perc_breed + se),
                  bioage_summ) +
  geom_vline(xintercept = bioage_senesce - 0.5, linetype = "dashed") +
  scale_y_continuous("Breeding", labels = scales::percent) +
  scale_color_manual(values = c("#7fbc41", "#de77ae")) +
  scale_fill_manual(values = c("#7fbc41", "#de77ae")) +
  labs(x = "Biological age (years-to-death)") +
  theme(legend.position = "none")

>>>>

ggplot(bioage_pred_pop, aes(bioage, predicted)) +
  geom_ribbon(aes(fill = bioage_cat, ymin = conf.low, ymax = conf.high), 
              alpha = 0.2) +
  geom_line(aes(color = bioage_cat), linewidth = 1.2, linetype = "dashed") +
  geom_line(aes(color = bioage_cat),
            bioage_pred_wgt, 
            linewidth = 1.2,
            linetype = "dotted") +
  geom_pointrange(aes(y = perc_breed, 
                      ymin = perc_breed - se, 
                      ymax = perc_breed + se),
                  bioage_summ) +
  geom_vline(xintercept = bioage_senesce - 0.5, linetype = "dashed") +
  scale_y_continuous("Breeding", labels = scales::percent, limits = c(.7, 1)) +
  scale_color_manual(values = c("#7fbc41", "#de77ae")) +
  scale_fill_manual(values = c("#7fbc41", "#de77ae")) +
  scale_x_continuous(limits = c(-17, 0)) + 
  labs(x = "Biological age (years-to-death)") +
  theme(legend.position = "none")
